Understanding Feedback Mechanisms in Machine Learning Jupyter Notebooks

### 2024-07-30 report/emse24.tex
feat(report): emse24 t2v updates

>>>>

The case studies conducted in RQ2 and RQ3 are subject to bias from the first author's individual perspective and understanding which could limit the interpretation of data and potentially overlook alternative viewpoints or explanations. To mitigate this threat, we implemented a rigorous review process involving multiple rounds of discussion with the second and third authors. These discussions continued until a consensus was reached on the interpretations and findings.
